---
title: "Long Term Lab Behavioral Summary"
output: html_document
---
```{r load necessary packages and dataframe, echo=FALSE}
library(ggplot2)
require(gridExtra)
require(lme4)
require(plyr)
#load data (refers to csv made by behavioral analysis script pulling directly from logfiles)
ltl = read.csv('~/Dropbox/LTLab/docs/LTL_AllLogs.csv',header=T)

ltl$srchand="L"
ltl$srchand[ltl$subNum %% 2 & ltl$runNum>4]="R"
ltl$srchand[!ltl$subNum %% 2 & ltl$runNum<=4]="R"
ltl$srchand = factor(ltl$srchand)

ltl$target[ltl$target=="Y"]="OLD"
ltl$target=factor(ltl$target)

ltl$rt=as.numeric(as.character(ltl$rt))
ltl$rt[ltl$rt==0]=NA

ltl$delay=factor(ltl$interval,labels=c("NEW","8mo","2mo","1hr"))
ltl$subID = factor(ltl$subNum)


```

```{r meanAndSem function, echo=F}
meanAndSem=function(x) c(mn = mean(x,na.rm=TRUE), se = sd(x,na.rm=T)/sqrt((sum(as.double(!is.na(x))))), len=sum(as.double(!is.na(x))))
```

*Cleaning Data* response excluded if:
<li>rt > 4s.
```{r clean RTs, echo=FALSE}
#for now, let's clean RTs equal to 0s, or longer than 4s
ltl$rt=as.numeric(as.character(ltl$rt))
ltl$rt[ ltl$rt>4]=NA
```
<li>a non repeat button is pressed (i.e. save 22, remove 23)
```{r clean unexpected responses, echo=FALSE}
#current strategy is to fix double responses (i.e. 33 and remove everything else, i.e. 34)
ltl$resp[ltl$resp==22]=2
ltl$resp[ltl$resp==33]=3
ltl$resp[ltl$resp==44]=4
ltl$resp[ltl$resp==77]=7
ltl$resp[ltl$resp==88]=8
ltl$resp[ltl$resp==99]=9
ltl$resp[!(ltl$resp %in% c(2,3,4,7,8,9))] = NA
#set all responses to correspond with left hands
newresp = ltl$resp
newresp[ltl$srchand=="R" & ltl$resp==3]=8
newresp[ltl$srchand=="R" & ltl$resp==4]=9
newresp[ltl$srchand=="R" & ltl$resp==7]=2
newresp[ltl$srchand=="R" & ltl$resp==8]=3
newresp[ltl$srchand=="R" & ltl$resp==9]=4
ltl$resp=newresp
ltl$resp[ltl$resp==7]=NA
#relabel these to get away from confusing numbers
leftkey = c("OBJ","FACE","SCENE","NEW","OLD")
ltl$resp = factor(ltl$resp, labels=leftkey)

```
Let's see what we had and then what we have left
```{r count response cats, echo=FALSE}
as.data.frame(table(ltl[,c("subID","delay")]))
as.data.frame(table(ltl[!is.na(ltl$resp),c("subID","delay")]))
```
Here's what we learn:
<li><s>subjects 8, 9, 12, 13, 14, & 16 have a couple "impossible" pictures categorized with target = NEW, but delay in (2mo or 1hr).</s> These have been fixed in the data frame. All were truly NEW, so the dataframe was modified to reflect this.
<li>subjects 8, & 13 are missing a bunch of responses



```{r add memory indicators to dataframe, echo=FALSE }
ltl$hit=as.numeric(ltl$target=="OLD" & ltl$resp %in% c("OLD","OBJ","FACE","SCENE"))
ltl$srcHit=as.numeric(ltl$target=="OLD" & as.character(ltl$picCat)==as.character(ltl$resp))
ltl$itemHit=as.numeric(ltl$target=="OLD" & ltl$resp=="OLD")
ltl$srcMiss=as.numeric(ltl$target=="OLD" & ltl$resp %in% c("OBJ","FACE","SCENE") & as.character(ltl$picCat)!=as.character(ltl$resp))
ltl$fa = as.numeric(ltl$target=="NEW" & ltl$resp %in% c("OLD","OBJ","FACE","SCENE"))
ltl$faItem = as.numeric(ltl$target=="NEW" & ltl$resp == 'OLD')
ltl$faSrc = as.numeric(ltl$target=="NEW" & ltl$resp %in% c("OBJ","FACE","SCENE"))
ltl$miss = as.numeric(ltl$target=="OLD" & ltl$resp=="NEW")
ltl$cr = as.numeric(ltl$target=="NEW" & ltl$resp=="NEW")
```

```{r create function to add accuracy to dataframe, echo=FALSE }
addMemCat = function(df){
  df$memType[df$srcHit==1]='Hit1-srcHit'
  df$memType[df$itemHit==1]='Hit3-itemOnly'
  df$memType[df$srcMiss==1]='Hit2-srcMiss'
  df$memType[df$cr==1]='CR'
  df$memType[df$faItem==1]='FA-item'
  df$memType[df$faSrc==1]='FA-src'
  df$memType[df$miss==1]='Miss'
  df$mem=df$memType
  df$mem[df$hit==1]='Hit'
  df$mem[df$fa==1]='FA'
  return(df)
}
```

```{r add single memCat col to ltl dataframe, echo=FALSE}
ltl=addMemCat(ltl)
```

```{r make old and new subsets, echo=FALSE }
ltlOld = subset(ltl,target=="OLD")
ltlOld$delay=factor(ltlOld$delay)
ltlHit=subset(ltlOld,hit==1)
ltlNew = subset(ltl,target=="NEW")
ltlNew$target=factor(ltlNew$target)
```

```{r errorbars maker, echo=FALSE}
errbars= aes(ymin=Freq[,"mn"]-Freq[,"se"],ymax=Freq[,"mn"]+Freq[,"se"])

```

---------
Let's look at some useful plots 

**Response Times by delay and memory class** 

```{r quick RTs, echo=FALSE}
rt_df = aggregate(cbind(rt)~delay+memType,ltl,meanAndSem)
ggplot(rt_df,aes(y=rt[,"mn"],x=delay,fill=memType))+geom_bar(stat='identity',position="dodge")+geom_errorbar(aes(ymin=rt[,"mn"]-rt[,"se"],ymax=rt[,"mn"]+rt[,"se"]),position=position_dodge(.9),width=.4)+labs(y="Response Time (s)",x="Delay")
```

**Response Frequencies by delay and memory class**

```{r response frequencies, echo=FALSE}
memTypeCounts=as.data.frame(table(ltlOld[!is.na(ltl$resp),c("subID","delay","memType")]))
oldCounts = as.data.frame(table(ltlOld[!is.na(ltl$resp),c("subID","delay")]))
memTypeCounts$Freq=memTypeCounts$Freq/oldCounts$Freq
memPlotDf = aggregate(Freq~memType+delay,memTypeCounts,meanAndSem)
memPlotDfSub = aggregate(Freq~memType+delay+subID,memTypeCounts,meanAndSem)
ggplot(memPlotDf,aes(x=delay,y=Freq[,"mn"],fill=memType))+geom_bar(stat='identity',position="dodge")+geom_errorbar(errbars,position=position_dodge(.9),width=.4)+labs(y="Frequency",x="Delay")
```

**Response Frequencies by delay and memory class *including FAs. note: color change***

```{r response frequencies with FAs, echo=FALSE}
memTypeCounts=as.data.frame(table(ltl[!is.na(ltl$resp),c("subID","delay","memType")]))
oldCounts = as.data.frame(table(ltl[!is.na(ltl$resp),c("subID","delay")]))
memTypeCounts$Freq=memTypeCounts$Freq/oldCounts$Freq
memTypeCounts$memType = factor(memTypeCounts$memType, levels=c("Hit1-srcHit","Hit2-srcMiss","Hit3-itemOnly","Miss","CR","FA-item","FA-src"))
memPlotDf = aggregate(Freq~memType+delay,memTypeCounts,meanAndSem)
memPlotDfSub = aggregate(Freq~memType+delay+subID,memTypeCounts,meanAndSem)
ggplot(memPlotDf,aes(x=delay,y=Freq[,"mn"],fill=memType))+geom_bar(stat='identity',position="dodge")+geom_errorbar(errbars,position=position_dodge(.9),width=.4)+labs(y="Frequency",x="Delay")
```

**d' by delay only** 

```{r d prime, echo=FALSE}
ltlNew = subset(ltl, target=="NEW")
farBySub = aggregate(fa~subID,ltlNew,meanAndSem)

hrBySub = aggregate(hit~subID,ltlOld,meanAndSem)
hrBySub$dprime = qnorm(hrBySub$hit[,"mn"])-qnorm(farBySub$fa[,"mn"])

hrBySubByDelay = aggregate(hit~subID+delay,ltlOld,meanAndSem)
hrBySubByDelay$dprime = qnorm(hrBySubByDelay$hit[,"mn"])-qnorm(farBySub$fa[,"mn"])

hrByDelay = aggregate(dprime~delay,hrBySubByDelay,meanAndSem)

ggplot(hrByDelay,aes(y=dprime[,"mn"],x=delay))+geom_bar(stat='identity',fill="white")+geom_point(data=hrBySubByDelay,aes(y=dprime,x=delay,color=subID),position=position_jitter(.05))+geom_errorbar(aes(ymin=dprime[,"mn"]-dprime[,"se"],ymax=dprime[,"mn"]+dprime[,"se"]),position=position_dodge(.9),width=.3)+labs(y="d'",x="Delay")
```

If needed, here's some code that may be helpful for doing error checking on the stimlists
```{r errorchecking code}
#requires that the input comes as two compiled csv. Easy to create using cat *0XX*study and cat *0XX*test in terminal
checkStudyTest = function(study, test){
  for ( i in 1:length(test$wordName)){
    word = as.character(test$wordName[i])
    test$found[i] = as.numeric(test$target[i]=="OLD")*as.numeric(length(study$wordName[study$wordName==as.character(word)])>0)
     }
  }
```
